О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
Minor fix

\begin{proof}
	We are interested in integral $t$ such that estimate~\eqref{eq:estimate_for_segment_length}
	yields to $b > 10000$, because we know the maximum quantity of points for integral point sets of diameters at most $10000$.
	So, let us consider $t\geq 647$ and find a coefficient $\gamma_2$,
	such that the inequality
	\begin{equation}
		\label{eq:inequality_for_linear_estimate_of_segment_length}
		\frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5 }{6}t^{1/2} \geq \frac{t-6}{\gamma_2}
	\end{equation}
	holds for all $t\geq 647$.
	For these $t$,
	the left part of~\eqref{eq:inequality_for_linear_estimate_of_segment_length} obviously grows faster than the right one.
	Turning~\eqref{eq:inequality_for_linear_estimate_of_segment_length} into the same equality
	and solving it for $t=647$, we obtain the claimed estimate.
\end{proof}

>>>>

\begin{proof}
	We are interested in integral $t$ such that estimate~\eqref{eq:estimate_for_segment_length}
	yields to $b > 10000$, because we know the maximum quantity of points for planar integral point sets of diameters at most $10000$.
	So, let us consider $t\geq 647$ and find a coefficient $\gamma_2$,
	such that the inequality
	\begin{equation}
		\label{eq:inequality_for_linear_estimate_of_segment_length}
		\frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5 }{6}t^{1/2} \geq \frac{t-6}{\gamma_2}
	\end{equation}
	holds for all $t\geq 647$.
	For these $t$,
	the left part of~\eqref{eq:inequality_for_linear_estimate_of_segment_length} obviously grows faster than the right one.
	Turning~\eqref{eq:inequality_for_linear_estimate_of_segment_length} into the same equality
	and solving it for $t=647$, we obtain the claimed estimate.
\end{proof}
